On the formation of H$\alpha$ line emission around classical T Tauri star: the disc-wind-magnetosphere hybrid model

### 2006-01-30 TTau_Halpha/kurosawa.tex
Minor change
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@645 25464f21-6099-402c-b30a-640f1d40d38b

\usepackage{babel}
\makeatother
\begin{document}
\title[On the formation of H$\alpha$ around classical T Tauri
  stars]{On the formation of H$\alpha$ line emission around classical
  T Tauri star: the disc-wind-magnetosphere hybrid models}

>>>>

\usepackage{babel}
\makeatother
\begin{document}
\title[On the formation of H$\alpha$ around classical T Tauri
  stars]{On the formation of H$\alpha$ line emission around classical
  T Tauri star: the disc-wind-magnetosphere hybrid model}
